\documentclass[11pt,a4paper]{letter}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\signature{Ignacio Diago Valeta}
\address{
Ignacio Diago Valeta\\
Vinalesa, Valencia, Spain\\
+34 645 98 70 21\\
\href{mailto:nadiva1243@gmail.com}{nadiva1243@gmail.com}\\
\href{https://www.linkedin.com/in/ignacio-diago-valeta-1234567891011121314/?locale=en_US}{LinkedIn}
}
\date{\today}

\begin{document}

\begin{letter}{Hiring Team}
\opening{Dear Hiring Team,}

I am a Computer Engineering student at Universitat Politecnica de Valencia and an AI \& Back-End Developer at Grupo Educativo CEU. I am writing to express my interest in opportunities where I can contribute to applied AI and software engineering projects with real impact.

In my current role, I design and deploy production AI solutions, including GPT-powered assistants and retrieval-augmented generation (RAG) pipelines connected to institutional data. I also build backend services that integrate cloud tools and automation workflows to improve daily operations. Alongside this work, I continue strengthening my engineering foundation through projects in machine learning, NLP, and scalable software design.

I would value the opportunity to bring this mix of academic rigor, practical AI development, and strong execution to your team. Thank you for your time and consideration. I would be glad to discuss how I can contribute.

\closing{Sincerely,}

\end{letter}
\end{document}
